Considering scale in multilayer animal social networks

### 2020-06-29 paper/manuscript.Rmd
results edits

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength was higher in foraging and open layers
than in forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased sharply between 5 m and 100 m in all three habitat classes followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allows [e.g. from this study and @Peignier_2019;
@Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
for studies in the field [@Lingle_2003; @Clutton_1982].

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals in foraging layers
at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent in forest and open layers
as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
with increasing spatial resolution, while decreasing in foraging habitat 
(`r count[res == 30 & lc == 3, percent]`% at 30 m
- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
indicate the importance of matching land cover resolution to scale of
habitat selection and choosing a land cover product with a resolution
sufficient to detect less common habitats.

The temporal multilayer network indicated within-year time windows where social
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and
15-20 than in time windows 2-5 and 12-15 (Figure \@ref(fig:temp) A). Time
windows of higher edge overlap, between approximately October and June, also had
higher graph strength compared to time windows of lower edge overlap, between
approximately June and October (Figure \@ref(fig:temp) C). Graph strength peaked
across the time series between January 2018 and April 2018. These results
highlight the importance of carefully selecting the temporal scale of analysis
to effectively capture within- and across-year variation in sociality.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. Edge
overlap increased across all three habitat layers with increasing number of
observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
individuals increased quickly between 10 and 100 observations, and continued to
increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
across individuals in all three habitat layers was highly variable at low number
of observations and variance decreased after ~100 observations (Figure
\@ref(fig:nobs) A). Since the variance in these multilayer metrics decreases
after a certain number of observations, this sensitivity method could be useful
for determining the number of observations necessary for sufficiently describing
social dynamics across contexts.

An illustrative multilayer network was generated, informed by previous social, 
spatial and temporal scale results (Figure \@ref(fig:ml)). <!--The social 
distance threshold was 50 m. The spatial resolution of the land cover 
raster was 30 m. -->Relocations were predominantly in open 
(`r count[res == 30 & lc == 1, percent]`%) and forest 
(`r count[res == 30 & lc == 2, percent]`%) habitats 
compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
Despite this, individuals were more strongly connected in foraging and open 
habitats than in forest (mean graph strength in habitat layers; foraging: 0.21, 
forest: 0.11, open: 0.23). There was a seasonal difference in association with 
individuals more connected between approximately October - June 
(mean graph strength in time windows; 2: 0.37, 4: 0.18) 
than between approximately June - October 
(mean graph strength in time windows; 1: 0.04, 3: 0.03). The time windows
were aggregated from the finer scale time windows presented above (time window 1:
2-5, time window 2: 6-11, time window 3: 12-15, time window 4: 16-20).

>>>>

# Results
Individuals in multilayer networks became more connected as the social distance
threshold increased. Mean graph strength was higher in foraging and open layers
compared to forest layers (Figure \@ref(fig:socres)). Individual graph strength
increased when the social distance threshold increased from 5 m and 100 m in 
all three habitat layers followed by
a plateau in the rate of increase after 100 m (Figure \@ref(fig:socres)). These
results suggest the optimal social scale at which groups should be assigned is
between ~20 - 100 m based on the rate at which variance in graph strength
decreased. GPS data allowed [e.g. from this study and @Peignier_2019;
@Lesmerises_2018] us to confirm the use of 50 m buffer that has long been used
for studies of ungulate social behaviour in the field [@Lingle_2003; @Clutton_1982].

Increasing land cover resolution resulted in decreased availability of foraging
habitat and corresponding low connectivity of individuals in foraging layers
at higher land cover
resolutions. Edge overlap decreased sharply between 30 m and 600 m in foraging
layers, afterwards remaining stable to 1000 m (Figure \@ref(fig:lcres) D). In
contrast, edge overlap was relatively consistent in forest and open layers
as land cover resolution increased (Figure \@ref(fig:lcres) D). Graph strength was more
variable within foraging habitat layers across land cover resolutions than open
and forest habitat layers (Figure \@ref(fig:lcres) E). The proportion of
relocations in forest (`r count[res == 30 & lc == 2, percent]`% at 30 m - 
`r count[res == 1000 & lc == 2, percent]`% at 1000 m) and open 
(`r count[res == 30 & lc == 1, percent]`% at 30 m - 
`r count[res == 1000 & lc == 1, percent]`% at 1000 m) habitats increased 
with increasing spatial resolution, while decreasing in foraging habitat 
(`r count[res == 30 & lc == 3, percent]`% at 30 m
- `r count[res == 1000 & lc == 3, percent]`% at 1000 m). These results 
indicated the importance of matching land cover resolution to scale of
habitat selection and choosing a land cover product with a resolution
sufficient to detect less common habitats.

The temporal multilayer network indicated within-year time windows where social
network metrics increased. Edge overlap was higher in time windows 1, 6-11 and
15-20 (between approximately October and June) than in time windows 2-5 and 12-15 
(between approximately June and October) (Figure \@ref(fig:temp) A). Time
windows of higher edge overlap also had
higher graph strength compared to time windows of lower edge overlap, between
approximately June and October (Figure \@ref(fig:temp) C). Graph strength peaked
across the time series throughout winter 2018 (January to April). These results
highlight the importance of carefully selecting the temporal scale of analysis
to effectively capture within- and across-year variation in sociality.

As the number of observations used to generate multilayer networks increased,
individuals became more connected and variance in metrics decreased. Edge
overlap increased across all three habitat layers with increasing number of
observations (Figure \@ref(fig:nobs) B). Similarly, multidegree for all
individuals increased quickly between 10 and 100 observations and continued to
increase until 1000 observations (Figure \@ref(fig:nobs) C). Graph strength
across individuals in all three habitat layers was highly variable at low number
of observations and variance decreased after ~100 observations (Figure
\@ref(fig:nobs) A). Since the variance in these multilayer metrics decreases
after a certain number of observations, this sensitivity method could be useful
for determining the number of observations necessary for sufficiently describing
social dynamics across contexts.

An illustrative multilayer network was generated, informed by previous social, 
spatial, and temporal scale results (Figure \@ref(fig:ml)). Relocations were predominantly in open 
(`r count[res == 30 & lc == 1, percent]`%) and forest 
(`r count[res == 30 & lc == 2, percent]`%) habitats 
compared to foraging habitats (`r count[res == 30 & lc == 3, percent]`%). 
Despite lower proportion of relocations in foraging habitat, 
individuals were more strongly connected in foraging and open 
habitats than in forest (mean graph strength in habitat layers (SD); foraging: 0.21 (0.23), 
forest: 0.11 (0.13), open: 0.23 (0.24)). There was a seasonal difference in association with 
individuals more connected between approximately October - June 
(mean graph strength in time windows; 2: 0.37 (0.23), 4: 0.18 (0.11)) 
than between approximately June - October 
(mean graph strength in time windows; 1: 0.04 (0.04), 3: 0.03 (0.07)). The time windows
were aggregated from the finer scale time windows presented above (time window 1:
2-5, time window 2: 6-11, time window 3: 12-15, time window 4: 16-20).
